---
title: "Check Backtracked Results v2"
author: "Andy Hartley"
date: "28 August 2014"
output:
  html_document:
    theme: journal
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(cache=TRUE)
source("functions/saveSpatial.R")
```

This is an Rmarkdown document to check the results from the latest version of the backtracking results. 

## Load Data

First, let's load the data

```{r}
library(knitr)
outresults_file <- "/Users/ajh235/Work/DataLocal/Projects/InternalSabbatical/Results/backtracked_results_1000km_5min.Rdata"
load(outresults_file)
bt_results$Hour <- as.numeric(format(bt_results$timestep, "%H"))
bt_results$Day <- as.numeric(format(bt_results$timestep, "%d"))
```

Get all the MCS that have IDs < 1502
```{r}
allmcs <- 1:1502
```

Which MCS *do* have a Generation point?
```{r}
genpt <- sort(allmcs[bt_results[bt_results$ID <= 1502 & bt_results$class == "Generation","ID"]])
length(unique(genpt))
```

Which MCS *don't* have a Generation point?
```{r}
nogenpts <- allmcs[-bt_results[bt_results$ID <= 1502 & bt_results$class == "Generation","ID"]]
length(unique(nogenpts))
```

## What happens to the MCS with no generation point?
```{r}
all_ngp_class <- vector("character")
for (ngp in nogenpts){
    # Get earliest record for this ID, and print class
    first_time <- min(bt_results[bt_results$ID == ngp, "timestep"])
    ft_class <- bt_results[bt_results$ID == ngp & bt_results$timestep == first_time, "class"]
    ft_related <- bt_results[bt_results$ID == ngp & bt_results$timestep == first_time, "related"]
    # print(paste("ID:",ngp, " Time:",first_time," Class:",ft_class," Related:",ft_related))
    ft_class <- sub("minor parts from ID [0-9]{1,6}", "minor parts", ft_class)
    all_ngp_class <- append(x = all_ngp_class, values = ft_class)
}
```

```{r results='asis'}
kable(as.data.frame(table(all_ngp_class)), format="markdown")
```

 * The majority (`r round(100*(412+38+33)/752)`%) are small parts of a split in the previous timestep - the largest overlap of the split takes the ID of the previous timestep, but the smaller parts need a new ID.
 * Some (`r round(100*(100+38+1)/752)`%) also dissipate after this timestep

## What is going on with the high ID numbers? 
```{r}
large_id <- sort(unique(bt_results[bt_results$ID > 1502,"ID"]))
all_lid_class <- vector("character")
end_lid_class <- vector("character")
for (lid in large_id){
    first_time <- min(bt_results[bt_results$ID == lid, "timestep"])
    last_time <- max(bt_results[bt_results$ID == lid, "timestep"])
    ft_class <- bt_results[bt_results$ID == lid & bt_results$timestep == first_time, "class"]
    ft_class <- sub("minor parts from ID [0-9]{1,6}", "minor parts", ft_class)
    lt_class <- bt_results[bt_results$ID == lid & bt_results$timestep == last_time, "class"]
    lt_class <- sub("minor parts from ID [0-9]{1,6}", "minor parts", lt_class)
    ft_related <- bt_results[bt_results$ID == lid & bt_results$timestep == first_time, "related"]
    # print(paste("ID:",lid, " Time:",first_time," Class:",ft_class," Related:",ft_related))
    all_lid_class <- append(x = all_lid_class, values = ft_class)
    end_lid_class <- append(x = end_lid_class, values = lt_class)
}
```

###For Large IDs (>1502) what classes are most common in the _first_ timestep?
```{r results='asis'}
kable(as.data.frame(100 * table(all_lid_class) / length(all_lid_class)), format="markdown")
```

 * 67% (2285) of the large numbers are POP generations
 * 31% (1034) are minor parts of splits in the current timestep


###For Large IDs (>1502) what classes are most common in the _last_ timestep?
```{r results='asis'}
kable(as.data.frame(100 * table(end_lid_class) / length(end_lid_class)), format="markdown")
```

 * 55% are merges in the next timestep, meaning that they merge into other 
 * 26% are generations, meaning that the last time step is also the first
 * 16% are minor parts of splits

###How many large IDs turn directly into MCS?
```{r}
table(bt_results[bt_results$ID %in% large_id,"type"])
```
 
 * Answer: 0
 * All results with a large ID (>1502) do not progress into MCS, although they may merge with other convective cells to form MCS. They either:
    + Die out straight after generation (26%). Or maybe they do not overlap in the second timestep - see above
    + or, they merge with larger cells (55%)

###How many large IDs can we remove because they generate and then dissipate before reaching the MCS threshold?
```{r}
# All large_id that have "Generation" at their last and first timestep
lid_gen_lt <- large_id[which(end_lid_class == "Generation")]
sp_data <- saveSpatial(bt_results[bt_results$ID %in% lid_gen_lt,],"largeIDs_gen_in_last_timestep")
```

So, there are `r length(lid_gen_lt)` large IDs that dissipate the timestep after they generate

###How many of each class once all of the '1 timestep' generations are removed?

```{r}
#knitr::opts_chunk$set(cache=FALSE) # Forces recalculation
lid_keep <- large_id[which(end_lid_class != "Generation")]
all_lid_class2 <- vector("character")
end_lid_class2 <- vector("character")
for (lid in lid_keep){
    first_time <- min(bt_results[bt_results$ID == lid, "timestep"])
    last_time <- max(bt_results[bt_results$ID == lid, "timestep"])
    ft_class <- bt_results[bt_results$ID == lid & bt_results$timestep == first_time, "class"]
    ft_class <- sub("minor parts from ID [0-9]{1,6}", "minor parts", ft_class)
    lt_class <- bt_results[bt_results$ID == lid & bt_results$timestep == last_time, "class"]
    lt_class <- sub("minor parts from ID [0-9]{1,6}", "minor parts", lt_class)
    all_lid_class2 <- append(x = all_lid_class2, values = ft_class)
    end_lid_class2 <- append(x = end_lid_class2, values = lt_class)
}
lid_ones <- as.numeric(attributes(which(table(bt_results[bt_results$ID %in% lid_keep,"ID"])==1))$names)
lid_ones_class <- bt_results[bt_results$ID %in% lid_ones,c("class")]
lid_ones_class <- sub("minor parts from ID [0-9]{1,6}", "minor parts", lid_ones_class)
```

```{r}
# Remove all POP (large IDs) that exist at only 1 timestep, and save the spatial data
lid_gen_lt <- large_id[which(end_lid_class == "Generation")]
bt_results_new <- bt_results[!(bt_results$ID %in% lid_gen_lt),]
bt_results_new$class <- sub("minor parts from ID [0-9]{1,6}", "minor parts", bt_results_new$class)
sp_data <- saveSpatial(bt_results_new,"bt_results_POP1t_removed")
save(bt_results_new, file="/Users/ajh235/Work/DataLocal/Projects/InternalSabbatical/Results/backtracked_results_1000km_5min_POP1t_removed.Rdata")
```


This is how they start ...

```{r results='asis'}
mydf_lid_start <- as.data.frame(round(100 * table(all_lid_class2) / length(all_lid_class2)))
colnames(mydf_lid_start) <- c("Class","%")
mydf_lid_start <- cbind(mydf_lid_start, Count=as.data.frame(table(all_lid_class2))$Freq)
kable(mydf_lid_start, format="markdown")
```

... and this is how they end ...
```{r results='asis'}
mydf_lid_end <- as.data.frame(round(100 * table(end_lid_class2) / length(end_lid_class2)))
colnames(mydf_lid_end) <- c("Class","%")
mydf_lid_end <- cbind(mydf_lid_end, Count=as.data.frame(table(end_lid_class2))$Freq)
kable(mydf_lid_end, format="markdown")
```



###What are the classes of the remainder that have 1 timestep only?

```{r results='asis'}
kable(as.data.frame(table(lid_ones_class)), format="markdown")
```


## Conclusions

1. We have `r length(unique(genpt))` MCS with generation points, and `r length(unique(nogenpts))` MCS without generation points. 

2. Where an MCS doesn't have a generation point, it has generally been created because a larger MCS split up, and the new ID is created from the smaller parts of the split.

3. Before convective cells reach the size threshold of an MCS, they can also split and merge. This creates new IDs (see IDs >1502), all of which are classified as POP. There are `r length(large_id)` unique IDs in this category, which contains a further `r length(bt_results[bt_results$ID %in% large_id & bt_results$class == "Generation","ID"])` initiations.

    + However, some of these initiations die out straight away (ie. the ID only exists for one timestep). There are `r length(lid_gen_lt)` points when this occurs.
    
    + Once these initiations are removed, there are `r length(all_lid_class2)` separate small scale convective cells (POP). 
    
    + Of these, `r mydf_lid_start[mydf_lid_start$Class == "Generation","%"]`% have generation points, the remainder are created when an existing POP splits, and the smaller part of the split receives a new ID.



